Challenges in Developing Great MCQMC Software

### 2022-07-13 MCQMC_2022_ChallengesDevelopSoftware.tex
Updates from Overleaf

\thanksnote{with Mark Klinchin and the rest of the GAIL an QMCPy teams \\
	partially supported by SigOpt, an Intel company \\[2ex]
	Thanks to the organizers as we meet again in person in still challenging times\\
	Slides at  \href{https://speakerdeck.com/fjhickernell/quasi-monte-carlo-software}{\nolinkurl{speakerdeck.com/fjhickernell/quasi-monte-carlo-software}}
}
\event{MCQMC 2022}
\date[]{July 18, 2022}

@@

>>>>

\thanksnote{with input from Mark Klinchin, the GAIL an QMCPy teams, and 
several friends \\
	partially supported by SigOpt, an Intel company \\[2ex]
	Thanks to the organizers as we meet again in person in still challenging times\\
	Slides at  \href{https://speakerdeck.com/fjhickernell/quasi-monte-carlo-software}{\nolinkurl{speakerdeck.com/fjhickernell/quasi-monte-carlo-software}}
}
\event{MCQMC 2022}
\date[]{July 18, 2022}

@@

\begin{frame}{Why Do We Need Software?}
\end{frame}

\begin{frame}{Brief History of MC\textbf{QMC} Software}
\end{frame}
